Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-08-23 Master Thesis/introduction.tex
Add acknowledgements

>>>>

I would like to thank my supervisor, Prof. Dr. Alexander Schmidt, for giving me such an interesting topic to pursue as my master thesis, and for all the insights and patient answers to all the countless questions I had.

I also wish to offer my thanks to all my friends, who supported me in this endeavor and encouraged me to go on. Last but not least, I am grateful for my parents who never ran out of patience with me.

This thesis was hard, arduous work, but, in the end, also very satisfying. And I couldn't have done it without you all. Thank you.
